Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-11-24 02_Paper/paper.tex
Fixed some grammar issues

Predictive analytics discover according to Delen and Damirkan explanatory and predictive patterns which represents 
the inherent relationships between data inputs and outputs, using data and mathematical techniques \cite{delen2013data}. 
This offers a wide range of applications. In the context of industrial or production enviroments, this includes in the areas of Processes, Products and Machines and Assets for example 
predictive maintenance, product design or optimization of routing and scheduling \cite{krauss2019machine}. 
Predictive analytics combined with quality control can be a powerful tool, because it is an improvement compared with the mentioned earlier currently
etablished quality control methods, in terms of speed, accuracy and time delay.
So far, only in exceptional cases in the literature is a combination of predictive analytics and quality control found \cite{aumi2012model, ritter1992neue}. With regard to general approaches to the use of predictive analytics,
for example in the form of machine learning in quality prediction, there is a lack in the literature. 
Related work, e.g from Krauß focused on automated machine learning for predictive quality in production \cite{krauss2020automated} and a product quality prediction in a process chain \cite{krauss2019machine}. 
The few existing approaches are extended by this paper in that a demonstrator executes an industry-unspecific production/assembly process,
the collection and processing of the data from the process parameters in continous and a few different ML algorithms are used for prediction, 
in order to determine, which algorithms are most advantageous for predicting the quality of an outcoming product. 
In addition, it is described in detail how the collected data was collected, prepared and processed.

@@

@@

In our work we applied a case-based research approach \cite{yin2017case} to answer the research question. 
One central motivation for a case-based research approach is to gain insights for real needs, rather than to develop theories without practical relevance \cite{cutcheon1993case}. %This sentence can be deleted if needed.
In addition case-based research approaches have already been successfully applied in the area of quality prediction based on process parameters (see, for example, ....). % @Lennart: hier müssen entsprechend Beispiele eingetragen werden
\AP{ 
       - How does the previous sentences apply to the democell?
       - This suits better in the methods section}

Our case of study is an abstraction of an assembly process at the industry. The industry 4.0 demonstration cell is composed by three independent conveyor belts, a robotic assembly arm, a laser scanner used for quality control as well as a wide range of sensors, all orchestrated by a SIEMENS PLC S7-1200. 
The assembly process done at this demostration cell consist on stacking two disk of different size on the top of each other. The quality of the pseudo products is later evaluated by the laser scanner by evaluating the concentricity of both disk. If the disk's concentricity is within a tolerance of 1.5mm, the piece is classified as OK, if not, it shall be classified as NOK.
By considering that malfunctions can occurs during real production processes at industries, our demonstration cell is able to simulate failures in diverse areas, such as:

\begin{itemize}
       \item Assemble errors due to robotic arm
       \item Bearing damage on the conveyor belt
       \item Resistance on the conveyor belt
       \item Leakage in the compressed air system
       \item Productivity limit reached
       \item Missing material
\end{itemize}

Those simulated failures have a real impact in the data collected by the sensors. Anomalies can be observed at the vibration sensors, temperature rise, fluctuations in the air pressure system, noticiable shifting on pieces' position as well as the stop of the process.

The continous data collection and clear correlation between the machine parameter is the ideal play-ground to implement a sandbox for machine learching implementations. With this in mind, our goal is to predict the quality of the product (concentricity of the assambled parts), prior to the actual quality check done by the laser scanner. The findings gained with the demonstration cell can be transferred to various real assembly processes and use cases, due to its manageable size and high degree of scalability. This would be an step forwards for future implementations at the industry, where the quality predictions might determine early enough, the next steps for the assambled pieces.

@@

\begin{figure}
       \includestandalone[width=.45\textwidth]{img/arm_data_plot}
       \caption{Robot arm movement patterns. We show the movement of the 
                cell's robot arm, its grippers and an encoding of the overall
                position in the system. The changes in the grip flag are triggered,
                when the gripper opens or closes. Zero indicates an open, while
                one indicates a closed gripper. The position flags marks the state
                of the cell's arm. 0 means the black disk is in store,
                one that the black disk is in the gate, two that the white disk
                is in store and three that the white disk is located in gate.
             }
\label{fig:robot_pos_cell}
\end{figure}

\AP{ @Moritz: Why is the figure 2 whithin the area of the Demozelle section?}

@@

\subsection{Recording the data}
\DSt{
- could we include collection via OPCUA server? or manually? 
}

@@

We compare a total of three different classifier architectures on the data.
A Support Vector Machine (SVM), a multilinear perceptron and a Random Forest
structure. All three methods are trained using standard hyperparameters.
\footnote{In order to allow exact reproduction of these results source
code is available at \url{https://github.com/manubrain/Demo-Cell-Classification}}
\begin{table}
       \centering
       \begin{tabular}{ c c }
              Support Vector Machine & 95.\% \\
              Multilinear Perceptron & 95.\% \\
              Random Forest          & 100.\%
       \end{tabular}
       \caption{Method comparison for our annomaly detection task 
                using the industry demo data test set.}
       \label{tab:class_comp}
\end{table}
Results are shown in table~\ref{tab:class_comp}. For 55 of the total 132 samples
quality measurements indicate a problem. This sets the 
baseline over the entire data set, that would be obtained by simply labeling all samples
as good. Over the entire data set, we require to classify more than 58.3\% of the data correctly.
The test set contains eight incorrect samples. We would therefore expect any naive classifier
to produce a 60\% accuracy, which we have to beat. In Table~\ref{tab:class_comp},
we observe that this is indeed the case for all three approaches evaluated here.
The random forest performed best in this case.

@@

- Connection problem between devices
- Missing tags  
- Interpretation of data: preprocessing   
   - What data is relevant?
- Data sample size
- ML implementation @Moritz

@@

\section*{Acknowledgments}
This project was partly supported by the german and european IKT.NRW
project "`ManuBrain"' 
\DSt{
do we need to include ManuBrain reference here?
}

>>>>

Predictive analytics discover according to Delen and Damirkan explanatory and predictive patterns which represents 
the inherent relationships between data inputs and outputs, using data and mathematical techniques \cite{delen2013data}. 
This offers a wide range of applications. In the context of industrial or production environments, this includes in the areas of Processes, Products and Machines and Assets for example 
predictive maintenance, product design or optimization of routing and scheduling \cite{krauss2019machine}. 
Predictive analytics combined with quality control can be a powerful tool because it is an improvement compared with the mentioned earlier currently
established quality control methods, in terms of speed, accuracy and time delay.
So far, only in exceptional cases in the literature is a combination of predictive analytics and quality control found \cite{aumi2012model, ritter1992neue}. With regard to general approaches to the use of predictive analytics,
for example in the form of machine learning in quality prediction, there is a lack in the literature. 
Related work, e.g from Krauß focused on automated machine learning for predictive quality in production \cite{krauss2020automated} and a product quality prediction in a process chain \cite{krauss2019machine}. 
The few existing approaches are extended by this paper in that a demonstrator executes an industry-unspecific production/assembly process,
the collection and processing of the data from the process parameters in continuous and a few different ML algorithms are used for prediction, 
in order to determine, which algorithms are most advantageous for predicting the quality of an outcoming product. 
In addition, it is described in detail how the collected data was collected, prepared and processed.

@@

\AP{ - Research Question and research hypotesis}

@@

In our work we applied a case-based research approach \cite{yin2017case} to answer the research question. 
One central motivation for a case-based research approach is to gain insights for real needs, rather than to develop theories without practical relevance \cite{cutcheon1993case}. %This sentence can be deleted if needed.
In addition case-based research approaches have already been successfully applied in the area of quality prediction based on process parameters (see, for example, ....). % @Lennart: hier müssen entsprechend Beispiele eingetragen werden
\AP{ 
       - To answer the question, we apply a case base research. Then explain 
}

Our case of study is an abstraction of an assembly process at the industry. The industry 4.0 demonstration cell is composed by three independent conveyor belts, a robotic assembly arm, a laser scanner used for quality control as well as a wide range of sensors, all orchestrated by a SIEMENS PLC S7-1200. 
The assembly process done at this demonstration cell consist on stacking two disks of different size on the top of each other. The quality of the pseudo products is later evaluated by the laser scanner by evaluating the concentricity of both disks. If the disk's concentricity is within a tolerance of 1.5mm, the piece is classified as OK, if not, it shall be classified as NOK.
By considering that malfunctions can occurs during real production processes at industries, our demonstration cell is able to simulate failures in diverse areas, such as:

\begin{itemize}
       \item Assemble errors due to the robotic arm
       \item Bearing damage on the conveyor belt
       \item Resistance on the conveyor belt
       \item Leakage in the compressed air system
       \item Productivity limit reached
       \item Missing material
\end{itemize}

Those simulated failures have a real impact in the data collected by the sensors. Anomalies can be observed at the vibration sensors, temperature rise, fluctuations in the air pressure system, noticeable shifting on pieces' position as well as the stop of the process.

The continuous data collection and the clear correlation between the machine parameter is the ideal play-ground to implement a sandbox for machine learning implementations. With this in mind, our goal is to predict the quality of the product (concentricity of the assembled parts), prior to the actual quality check done by the laser scanner. The findings gained with the demonstration cell can be transferred to various real assembly processes and use cases, due to its manageable size and the high degree of scalability. This would be a step forwards for future implementations at the industry, where the quality predictions might determine early enough, the next steps for the assembled pieces.

@@

\begin{figure}
       \includestandalone[width=.45\textwidth]{img/arm_data_plot}
       \caption{Robot arm movement patterns. We show the movement of the 
                cell's robot arm, its grippers, and the encoding of the overall
                position in the system. The changes in the grip flag are triggered,
                when the gripper opens or closes. Zero indicates an open, while
                one indicates a closed gripper. The position flags marks the state
                of the cell's arm. 0 means the black disk is in store,
                one that the black disk is at the gate, two that the white disk
                is in store and three that the white disk is located at the gate.
             }
\label{fig:robot_pos_cell}
\end{figure}

\AP{ @Moritz: Why is figure 2 within the area of the Demozelle section?}

@@

\subsection{Recording the data} %collecting the data
\DSt{
- could we include collection via OPCUA server? or manually? 
}

\AP{
       - AUExpert manually/ automated
}

@@

We compare a total of three different classifier architectures on the data.
A Support Vector Machine (SVM), a multilinear perceptron and a Random Forest
structure. All three methods are trained using standard hyperparameters.
\footnote{In order to allow exact reproduction of these results source
code is available at \url{https://github.com/manubrain/Demo-Cell-Classification}}
\begin{table}
       \centering
       \begin{tabular}{ c c }
              Support Vector Machine & 95.\% \\
              Multilinear Perceptron & 95.\% \\
              Random Forest          & 100.\%
       \end{tabular}
       \caption{Method comparison for our anomaly detection task 
                using the industry demo data test set.}
       \label{tab:class_comp}
\end{table}
Results are shown in table~\ref{tab:class_comp}. For 55 of the total 132 samples
quality measurements indicate a problem. This sets the 
baseline over the entire data set, that would be obtained by simply labeling all samples
as good. Over the entire data set, we require to classify more than 58.3\% of the data correctly.
The test set contains eight incorrect samples. We would therefore expect any naive classifier
to produce a 60\% accuracy, which we have to beat. In Table~\ref{tab:class_comp},
we observe that this is indeed the case for all three approaches evaluated here.
The random forest performed best in this case.

@@

- Connection problem between devices
   - Network connection
   - Device restriction: SIM4000, SIEMENS. 
   - Server Timestamp syncr.
- Missing data tags: modifying PLC and robot code to have tags
- Interpretation of data: preprocessing
   - What data is relevant?
- Data sample size
- ML implementation @Moritz

@@

\section*{Acknowledgments}
This project was partly supported by the german and european IKT.NRW
project "ManuBrain"
\DSt{
do we need to include ManuBrain reference here?
}
\AP{
Expand EFRE @stn
}
